---
title: "My first R Markdown"
author: "Sergio Alexander Torres Palomares"
date: "5/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown basic description

With R Markdown we can write texts, articles, books or our data Reports.
One of the best resources of using R Markdown is that we can **Output** our
writings with different text formats like: 

- *PDF*  
- *LATEX*  
- *WORD*  
- *SLIDES*  

Another important resource that is really important to identify is the acces
to insert **Codes Chunks** , with this it is possible to put plots or tables
made by code lines like the next one.

#### *Example*
```{r echo=FALSE}
print("Hello world")
print("This is an easy code line wrote in order to demostrate")
print("The use of the Code Chunk")
```
If there are questions about the use of R Markdown, a little review [1] about 
some basic but important line codes was inserted however, to obtain more 
information here <http://rmarkdown.rstudio.com>  is the link of the official 
page were it can be found **tutorials**, **lessons** or **books**.

### [1] Important R Markdown Line Codes
- *Bold*
- **Italics**
- [Link]  
 



